---
title: "ds_sociodemographic compare full vs SRS"
author: "Josh Alampi"
date: "2024-10-25"
output: html_document
---


# load
```{r}
#clear workspace
rm(list=ls(all=TRUE))

# load packages and functions
source("libraries.R", echo = T)
source("functions/analysis functions.R")

# Load MIREC data
data_all <- read.csv("//ais-fs1.sfu.ca/home2/Redirected_Profiles/jalampi/Desktop/MIREC loader 2022/clean data/MIREC data_mixtures.csv") %>% 
  filter(live.birth2 == 1 & num.babies3 == 1) %>% 
  clean_data(mice_filter = F) 
  
data <- data_all %>% 
  filter(is.na(srs) == F) 

```

# clean data

## Edit 'data_no_srs' to only include participants without an SRS-score
```{r}
ids_with_srs <- data$subject.id
ids_all <- data_all$subject.id

ids_without_srs <- setdiff(ids_all, ids_with_srs)


data_no_srs <- data_all %>% 
  filter(subject.id %in% ids_without_srs)
```



## make new variable: home.score2 (binary variable) 
```{r include=FALSE}
median_home <- quantile(data$home.score, 0.5, na.rm = T)
median_srs_age <- quantile(data$srs.age, 0.5)


data <- data %>% 
  mutate(home.score2 = ifelse(home.score >= median_home, 1, 0)) %>% # Make HOME score a binary variable
  mutate(srs.age2 = ifelse(srs.age >= median_srs_age, 1, 0)) %>% # Make SRS age a binary variable
  mutate(all = 1) # make a variable where all participants are coded as == 1. 

data_no_srs <- data_no_srs %>% 
  mutate(home.score2 = ifelse(home.score >= median_home, 1, 0)) %>% # Make HOME score a binary variable
  mutate(srs.age2 = ifelse(srs.age >= median_srs_age, 1, 0)) %>% # Make SRS age a binary variable
  mutate(all = 1) # make a variable where all participants are coded as == 1. 

# prep for comparison of full and subset datasets
data_no_srs$dataset <- "Full"
data$dataset <- "Subset"

# Combine the two datasets
combined_data <- rbind(data_no_srs, data)
```

## Fix data_no_srs folate concentration variables
```{r}
# Calculate the folate percentiles based on the dataset used in the analysis (the ppl with SRS scores)
tot_fol.t1_10 <- quantile(data$tot_fol.t1, 0.1, na.rm = T)
tot_fol.t1_80 <- quantile(data$tot_fol.t1, 0.8, na.rm = T)
umfa.t1_80 <- quantile(data$umfa.t1.res, 0.8, na.rm = T)

# Ensure that the cutoffs used in the 'full' dataset are the same as the dataset used in the analysis
data_no_srs <- data_no_srs %>% 
  select(-c(pl_fol3.t1, umfa2.t1)) %>% 
  dplyr::mutate(pl_fol3.t1 = case_when(tot_fol.t1 < tot_fol.t1_10 ~ 1,
                                       tot_fol.t1 > tot_fol.t1_80 ~ 3,
                                       is.na(tot_fol.t1) ~ NA,
                                       .default = 2)) %>% # Between 10th and 80th %ile is assigned 2
  dplyr::mutate(umfa2.t1 = ifelse(umfa.t1.res > umfa.t1_80,
                                  1, # ppl w/ umfa conc. above 80th percentile assigned 1
                                  0)) # otherwise they are assigned 2

```

# Check data
```{r}
summary(data_no_srs$all)
summary(data_no_srs$sex2)
summary(data_no_srs$living.status2)
summary(data_no_srs$race.white2)
summary(data_no_srs$edu4)
summary(data_no_srs$income4)
summary(data_no_srs$parity3)
summary(data_no_srs$home.score2)
summary(data_no_srs$smoker2)
summary(data_no_srs$fish3)
summary(data_no_srs$fol.intake3)
summary(data_no_srs$pl_fol3.t1)
summary(data_no_srs$umfa2.t1)

```

#make functions
## desciptive statistics
```{r include=FALSE}
get_ds <- function(data, var, level, name, round = 1, roundchem = 2) {
  tot_n <- nrow(data)
  if(level == "NA"){
    subset_data <- filter(data, is.na({{var}}) == T)
  } else {
    subset_data <- filter(data, {{var}} == {{level}})
  }
  
  n <- nrow(subset_data)
  perc <- format(round(n/tot_n*100, round), nsmall = round)
  
  srs_mean <- format(round(mean(subset_data$srs), round), nsmall = round)
  srs_sd <-format(round(sd(subset_data$srs), round), nsmall = round)
  
  if(level == "NA"){
    srs_mean <- paste0("")
    srs_sd <-paste0("")
    
  }
  
  mat <- matrix(data=NA, nrow = 1, ncol = 3)
  mat[1,1] <- ifelse(name == "All", 
                     paste0(name),
                     paste0("   ", name))
  
  mat[1,2] <- paste0(n, " (", perc, ")")
  
  mat[1,3] <- ifelse(level == "NA",
                     paste0(""),
                     paste0(srs_mean, " (", srs_sd, ")"))
  
  return(mat)
}
```

test:
```{r}
get_ds(data, sex2, 0, "Male")
```

# make table1 (with SRS data)
```{r include=FALSE}
table1 <- setNames(data.frame(matrix(data = "", nrow = 49, ncol = 3)), #make dataframe
                              c("Variable", "n (%)", "Mean SRS-2 score (SD)")) #set column names

i <- 1

table1[i,] <- get_ds(data, all, 1, "All"); i <- i + 1

table1[i,1] <- "Child sex"; i <- i + 1
table1[i,] <- get_ds(data, sex2, 0, "Male"); i <- i + 1
table1[i,] <- get_ds(data, sex2, 1, "Female"); i <- i + 1
table1[i,] <- get_ds(data, sex2, "NA", "Missing"); i <- i + 1

table1[i,1] <- "Maternal age at enrollment (years)"; i <- i + 1
table1[i,] <- get_ds(data, mom.age3, 1, "18 - 29"); i <- i + 1
table1[i,] <- get_ds(data, mom.age3, 2, "30 - 35"); i <- i + 1
table1[i,] <- get_ds(data, mom.age3, 3, "≥36"); i <- i + 1

table1[i,1] <- "Living with partner"; i <- i + 1
table1[i,] <- get_ds(data, living.status2, 0, "Yes"); i <- i + 1
table1[i,] <- get_ds(data, living.status2, 1, "No"); i <- i + 1

table1[i,1] <- "Maternal race"; i <- i + 1
table1[i,] <- get_ds(data, race.white2, 1, "White"); i <- i + 1
table1[i,] <- get_ds(data, race.white2, 0, "Other"); i <- i + 1

table1[i,1] <- "Education level"; i <- i + 1
table1[i,] <- get_ds(data, edu4, 1, "High school or less"); i <- i + 1
table1[i,] <- get_ds(data, edu4, 2, "College or trade school"); i <- i + 1
table1[i,] <- get_ds(data, edu4, 3, "Undergraduate university degree"); i <- i + 1
table1[i,] <- get_ds(data, edu4, 4, "Graduate university degree"); i <- i + 1
table1[i,] <- get_ds(data, edu4, "NA", "Missing"); i <- i + 1

table1[i,1] <- "Annual household income ($CAD)"; i <- i + 1
table1[i,] <- get_ds(data, income4, 1, "≤$40,000"); i <- i + 1
table1[i,] <- get_ds(data, income4, 2, "$40,001 - $80,000"); i <- i + 1
table1[i,] <- get_ds(data, income4, 3, "$80,001 - $100,000"); i <- i + 1
table1[i,] <- get_ds(data, income4, 4, ">$100,000"); i <- i + 1
table1[i,] <- get_ds(data, income4, "NA", "Missing"); i <- i + 1

table1[i,1] <- "Parity"; i <- i + 1
table1[i,] <- get_ds(data, parity3, 1, "Nulliparous"); i <- i + 1
table1[i,] <- get_ds(data, parity3, 2, "Uniparous"); i <- i + 1
table1[i,] <- get_ds(data, parity3, 3, "Multiparous"); i <- i + 1

table1[i,1] <- "HOME score"; i <- i + 1
table1[i,] <- get_ds(data, home.score2, 1, "≥48 (median)"); i <- i + 1
table1[i,] <- get_ds(data, home.score2, 0, "<48 (median)"); i <- i + 1
table1[i,] <- get_ds(data, home.score2, "NA", "Missing"); i <- i + 1

table1[i,1] <- "Smoked during pregnancy"; i <- i + 1
table1[i,] <- get_ds(data, smoker2, 1, "Yesᵃ"); i <- i + 1
table1[i,] <- get_ds(data, smoker2, 0, "No"); i <- i + 1
table1[i,] <- get_ds(data, smoker2, "NA", "Missing"); i <- i + 1

table1[i,1] <- "First trimester fish consumption"; i <- i + 1
table1[i,] <- get_ds(data, fish3, 1, "0-2 times per month"); i <- i + 1
table1[i,] <- get_ds(data, fish3, 2, "3-7 times per month"); i <- i + 1
table1[i,] <- get_ds(data, fish3, 3, "≥8 times per month"); i <- i + 1
table1[i,] <- get_ds(data, fish3, "NA", "Missing"); i <- i + 1

table1[i,1] <- "Folic acid supplementationᵇ"; i <- i + 1
table1[i,] <- get_ds(data, fol.intake3, 1, "<400 µg per day"); i <- i + 1
table1[i,] <- get_ds(data, fol.intake3, 2, "400 - 1000 µg per day"); i <- i + 1
table1[i,] <- get_ds(data, fol.intake3, 3, ">1000 µg per day"); i <- i + 1

table1[i,1] <- "Plasma total folate concentrationsᶜ"; i <- i + 1
table1[i,] <- get_ds(data, pl_fol3.t1, 1, "<10ᵗʰ percentile (65.6 nmol/L)"); i <- i + 1
table1[i,] <- get_ds(data, pl_fol3.t1, 2, "10ᵗʰ - 80ᵗʰ percentile"); i <- i + 1
table1[i,] <- get_ds(data, pl_fol3.t1, 3, ">80ᵗʰ percentile (125 nmol/L)"); i <- i + 1
table1[i,] <- get_ds(data, pl_fol3.t1, "NA", "Missing"); i <- i + 1

table1[i,1] <- "Unmetabolized folic acid concentrations"; i <- i + 1
table1[i,] <- get_ds(data, umfa2.t1, 0, "≤80ᵗʰ percentile"); i <- i + 1
table1[i,] <- get_ds(data, umfa2.t1, 1, ">80ᵗʰ percentile (13.6 nmol/L)"); i <- i + 1
table1[i,] <- get_ds(data, umfa2.t1, "NA", "Missing"); i <- i + 1

i
```

# make table1s (with singleton live births)
```{r include=FALSE}
table1s <- setNames(data.frame(matrix(data = NA, nrow = 49, ncol = 4)), #make dataframe
                    c("Variable", "n (%)", "Mean SRS-2 score (SD)", "p")) #set column names

i <- 1

table1s[i,1:3] <- get_ds(data_no_srs, all, 1, "All"); i <- i + 1

table1s[i,1] <- "Child sex"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$sex2))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, sex2, 0, "Male"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, sex2, 1, "Female"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, sex2, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "Maternal age at enrollment (years)"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$mom.age3))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, mom.age3, 1, "18 - 29"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, mom.age3, 2, "30 - 35"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, mom.age3, 3, "≥36"); i <- i + 1

table1s[i,1] <- "Living with partner"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$living.status2))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, living.status2, 0, "Yes"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, living.status2, 1, "No"); i <- i + 1

table1s[i,1] <- "Maternal race"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$race.white2))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, race.white2, 1, "White"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, race.white2, 0, "Other"); i <- i + 1

table1s[i,1] <- "Education level"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$edu4))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, edu4, 1, "High school or less"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, edu4, 2, "College or trade school"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, edu4, 3, "Undergraduate university degree"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, edu4, 4, "Graduate university degree"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, edu4, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "Annual household income ($CAD)"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$income4))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, income4, 1, "≤$40,000"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, income4, 2, "$40,001 - $80,000"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, income4, 3, "$80,001 - $100,000"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, income4, 4, ">$100,000"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, income4, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "Parity"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$parity3))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, parity3, 1, "Nulliparous"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, parity3, 2, "Uniparous"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, parity3, 3, "Multiparous"); i <- i + 1

table1s[i,1] <- "HOME score"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$home.score2))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, home.score2, 1, "≥48 (median)"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, home.score2, 0, "<48 (median)"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, home.score2, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "Smoked during pregnancy"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$smoker2))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, smoker2, 1, "Yesᵃ"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, smoker2, 0, "No"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, smoker2, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "First trimester fish consumption"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$fish3))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fish3, 1, "0-2 times per month"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fish3, 2, "3-7 times per month"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fish3, 3, "≥8 times per month"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fish3, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "Folic acid supplementationᵇ"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$fol.intake3))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fol.intake3, 1, "<400 µg per day"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fol.intake3, 2, "400 - 1000 µg per day"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, fol.intake3, 3, ">1000 µg per day"); i <- i + 1

table1s[i,1] <- "Plasma total folate concentrationsᶜ"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$pl_fol3.t1))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, pl_fol3.t1, 1, "<10ᵗʰ percentile (65.6 nmol/L)"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, pl_fol3.t1, 2, "10ᵗʰ - 80ᵗʰ percentile"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, pl_fol3.t1, 3, ">80ᵗʰ percentile (125 nmol/L)"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, pl_fol3.t1, "NA", "Missing"); i <- i + 1

table1s[i,1] <- "Unmetabolized folic acid concentrations"
table1s[i,4] <- chisq.test(table(combined_data$dataset, combined_data$umfa2.t1))$p.value; i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, umfa2.t1, 0, "≤80ᵗʰ percentile"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, umfa2.t1, 1, ">80ᵗʰ percentile (13.6 nmol/L)"); i <- i + 1
table1s[i,1:3] <- get_ds(data_no_srs, umfa2.t1, "NA", "Missing")

i

```

## Round p-values
```{r}
table1s <- table1s %>% 
  mutate(formatted_p = case_when(
    p <= 0.99 & p > 0.05 ~ format(round(p, 2), nsmall = 2),
    p <= 0.05 & p >= 0.01 ~ paste0(format(round(p, 2), nsmall = 2), "*"),
    p < 0.01 & p >= 0.001 ~ paste0(format(round(p, 3), nsmall = 3), "*"),
    p < 0.001 ~ "p < .001*"))
```


## put them together
Only need to report n and %. Since the mean SRS score will be the same for the both groups, I will not report it in this table. (once I remove all of the people who are NA for the SRS variable in the "full" n=1862 dataset, I am left with the same 601 participants who are in the "SRS-only" dataset) 
```{r}
# merge
table_all <- cbind(table1[,1:2], table1s[,c(2,5)])

# fix column names
colnames(table_all)[2] <- "Study sample (mother-child pairs with an SRS-2 score)_n (%)"
colnames(table_all)[3] <- "Full sample (singleton live births) without an SRS-2 score_n (%)"
colnames(table_all)[4] <- "p"

# Fix some labels
table_all[50,1] <- "   <65.6 nmol/L"
table_all[51,1] <- "   ≥65.6 nmol/L & ≤125 nmol/L"
table_all[52,1] <- "   >125 nmol/L"
table_all[55,1] <- "   ≤13.6 nmol/L"
table_all[56,1] <- "   >13.6 nmol/L"

table_all[54,1] <- "Unmetabolized folic acid concentrationsᵈ" # add a "c" superscript
```




# Make flextables

```{r}

title_table1s <- "Table S1. Comparison of study and full sample's sociodemographic characteristics, MIREC study, Canada, 2008-11."

footer_table1s <- "*: Denotes a Chi-square (comparing the study and full sample) test P-value less than 0.05. All P-values are two-sided.\n a: Includes current smokers and individuals who quit during pregnancy. 'Non-smoker' includes participants who did not smoke and former smokers. \n b: Folic acid supplementation was primarily measured via a survey conducted at 16 weeks gestation, which queried intake in the past 30 days. We also used data from the 24-hour recall version of this survey and a questionnaire completed at study enrollment (6-13 weeks gestation). \n c: Sum of 5-formyl-THF, 5-10-methylene-THF, THF, UMFA, 5-methyl-THF. 65.6 nmol/L and 125 nmol/L are the 10th and 80th percentiles of plasma total folate concentrations in the study sample. \n d: 13.6 nmol/L is the 80th percentile of unmetabolized folic acid concentrations in the study sample. \nAbbreviations: CAD, Canadian dollar; HOME, Home Observation for Measurement of the Environment; MIREC, Maternal-Infant Research on Environmental Chemicals Study; SD, Standard Deviation; SRS, Social Responsiveness Scale."

```



# Table 1s
```{r}
flextable_table1s <- table_all %>% 
  flextable() %>% 
  separate_header() %>% 
  add_header_lines(title_table1s) %>% 
  add_footer_lines(footer_table1s) %>% 
  
  # align header
  align(align = "center", part = "header") %>%
  align(align = "left", part = "header", j = 1) %>%
  
  set_table_properties(layout = "autofit", width = 1)

flextable_table1s
```


# Save

# Save table as a MS excel file
```{r}
write_xlsx(table_all, here::here("output", "ds", "ds_sociodemographics_compare_.xlsx"))

file_name <- paste0("ds_sociodemographics_compare_", Sys.Date(), ".xlsx")
write_xlsx(table_all, here::here("output", "ds", "archive", file_name)) # for archival purposes
```

## Save flextable as a word document
```{r echo=FALSE}
# Save flextable(s) as a .docx (Word) file
save_as_docx(flextable_table1s, # save these table(s)
             path = "output/table S_comparison.docx")

save_as_docx(flextable_table1s, # save these table(s)
             path = paste0("output/ds/archive/table S_comparison.", "_",  Sys.Date(), ".docx", sep = ""))
```

```{r}

```

