---
title: "Finding aux variables"
author: "Josh Alampi"
date: "2024-06-12"
output: html_document
---

# Notes
In this file I will attempt to identify 'auxiliary variables' to aid in the imputation of variables in my analysis that have missing data. An auxiliary variable should either:
Condition i)  Be associated with a variable I want to impute, or
Condition ii) Be associated with the probability of missingness of a variable I want to impute

The variables I want to impute are:
i)   All chemical concentrations (they all have some degree of missing data)
ii)  Categorical first trimester plasma total folate concentrations
iii) Income, education, and HOME score


# load
```{r}
#clear workspace
rm(list=ls(all=TRUE))

# load packages and functions
source(here::here("libraries.R"))
source("functions/ggplot functions.R")
source("functions/analysis functions.R")

# Load MIREC data
data <- read.csv("//ais-fs1.sfu.ca/home2/Redirected_Profiles/jalampi/Desktop/MIREC loader 2022/clean data/MIREC data_mixtures.csv") %>% 
  filter(is.na(srs) == F) %>% 
  clean_data(mice_filter = F)

data$mom.birthplace5 <- factor(data$mom.birthplace5, levels= c(1,2,3,4,5)) # born in Canada is reference

# Make function for standardizing values
standardize <- function(value) {
  stan_value <- (value - mean(value, na.rm = T)) / sd(value, na.rm = T)
}
## By putting all variables on the same scale I will have an easier time comparing them
```

# Selecting imputed variables
To simplify this process, I will evaluate the following imputed variables:
i)   All chemicals
ii)  *Continuous* first trimester plasma total folate concentrations 
iii) HOME scores

I will only consider continuous imputed variables here to greatly simplify this process. I believe I can omit the following categorical variables:
i) Categorical first trimester plasma total folate concentrations
-- because the continuous version of this variable is related to it. 

ii) Income 
-- because HOME score and many chemical concentrations are related to income. 

iii) Education 
-- for same reason as income. 

```{r}
impute_vars <- data %>% 
    dplyr::select(c(arsenic.t1.res, cadmium.t1.res, lead.t1.res, mercury.t1.res, # chemicals
                  bbhc.t1.res, dde.t1.res, oxychlor.t1.res, transnona.t1.res,
                  pfhxs.t1.res, pfos.t1.res, pfoa.t1.res,
                  pcb118.t1.res, pcb138.t1.res, pcb153.t1.res, pcb180.t1.res,
                  bde47.t1.res,
                  tot_fol.t1, home.score)) %>% 
  mutate_all(funs(standardize(.)))
```

# Selecting candidate auxilliary variables
I will consider the following auxiliary variables that I think could meet the above conditions:
1) birth weight
2) gestational age
3) alcohol consumption during pregnancy (yes/ no)
4)  Pre-pregnancy BMI
5) *Continuous* third trimester plasma total folate concentrations 
6) *Continuous* FA supplementation

7) Maternal birthplace
-- This variable is categorical, so I will handle it in a separate analysis

```{r}
aux_vars <- data %>% 
  select(c(birth.wt, gest.age, alc2, prepreg.bmi,
           tot_fol.t3, fol.intake)) %>% 
  mutate_all(funs(standardize(.))) 
```

# Condition i
## Test of association

### Correlation analyis
I will find the correlation between all imputed variables and all of the continuous candidate auxiliary variables. I like correlation because -1 <= correlation <= 1, while the effect estimate from a linear regression analysis can range from -infinity to +infinity, so it is harder to come up with a cutoff for when a relationship is notable. 

I will consider a given imputed variable and a given auxiliary variable to be associated with each other (and therefore satisfy criteria I at the top of the page) if they either:
i)  Have an absolute correlation value >= 0.2, or
ii) Have an adjusted p-value for correlation < 0.05. (adjusted for the number of candidate continuous auxiliary variables * the number of imputed variables)

```{r}
table_cor <- setNames(data.frame(matrix(data = NA, nrow = (6 * 18), ncol = 6)), #make dataframe
                                        c("aux_name", "impute_name", "correlation coef.", 
                                          "p", "p_adj", "flag")) #set column names
n_compare <- 6 * 18

for(i in 1:length(aux_vars)){
  aux_var <- aux_vars[[i]]
  
  for(j in 1:length(impute_vars)){
    impute_var <- impute_vars[[j]]
    
    cor <- cor(aux_var, impute_var, use = "complete.obs")
    cor_p <- cor.test(aux_var, impute_var)$p.value
    cor_padj <- p.adjust(cor_p, n = n_compare)
    
    p_flag <- ifelse(cor_padj < 0.05, T, 
                     ifelse(abs(cor) > 0.2, T, F))
    
    table_cor[(i - 1) * length(impute_vars) + j, 1] <- colnames(aux_vars)[i]
    table_cor[(i - 1) * length(impute_vars) + j, 2] <- colnames(impute_vars)[j]
    table_cor[(i - 1) * length(impute_vars) + j, 3] <- round(cor, 3)
    table_cor[(i - 1) * length(impute_vars) + j, 4] <- cor_p
    table_cor[(i - 1) * length(impute_vars) + j, 5] <- cor_padj
    table_cor[(i - 1) * length(impute_vars) + j, 6] <- p_flag
  }
}

table_cor
```

#### Selected aux vars
The following met the above criteria: birth weight, gestational age, alcohol, prepregnancy BMI,  third trimester plasma total folate concentrations, and continuous FA supplementation. 
So all of them were selected. 
```{r}
filter(table_cor, flag == T)$aux_name
```

### linear regression analysis
Mother's birthplace is categorical, so it will not work so well with the above correlation analysis. So I will run a linear regression model instead where the imputed variable is the outcome and mother's birthplace is the explanatory variable. 

I will consider a given imputed variable and a mother's birthplace to be associated with each other (and therefore satisfy criteria I at the top of the page) if they either:
i)  Have a beta >1 (a given birthplace is associated with a 2-SD change in the imputed variable)
ii) Have an adjusted p-value < 0.05. (adjusted for the number of candidate continuous auxilliary variables * the 5 levels of the mother's birthplace variable)

## mom birthplace
```{r}
table_birthplace <- setNames(data.frame(matrix(data = NA, nrow = 90, ncol = 6)), #make dataframe
                  c("aux_name", "impute_name", 
                    "Country", "Beta", 
                    "p", "p_adj")) #set column names

n_compare <- 18 * 5

for(i in 1:length(impute_vars)){
  impute_var <- impute_vars[[i]]
  
  model <- lm(impute_var ~ data$mom.birthplace5)
  coef <- coef(summary(model))
  
  table_birthplace[(i - 1) * 4 + 1, 1] <- "mom.birthplace5"
  table_birthplace[(i - 1) * 4 + 1, 2] <- colnames(impute_vars)[i]
  table_birthplace[(i - 1) * 4 + 1, 3] <- "US"
  table_birthplace[(i - 1) * 4 + 1, 4] <- round(coef[2,1], 2)
  table_birthplace[(i - 1) * 4 + 1, 5] <- coef[2,4]
  table_birthplace[(i - 1) * 4 + 1, 6] <- p.adjust(coef[2,4], n = n_compare)
  
  table_birthplace[(i - 1) * 4 + 2, 1] <- "mom.birthplace5"
  table_birthplace[(i - 1) * 4 + 2, 2] <- colnames(impute_vars)[i]
  table_birthplace[(i - 1) * 4 + 2, 3] <- "Mexico"
  table_birthplace[(i - 1) * 4 + 2, 4] <- round(coef[3,1], 2)
  table_birthplace[(i - 1) * 4 + 2, 5] <- coef[3,4]
  table_birthplace[(i - 1) * 4 + 2, 6] <- p.adjust(coef[3,4], n = n_compare)
  
  table_birthplace[(i - 1) * 4 + 3, 1] <- "mom.birthplace5"
  table_birthplace[(i - 1) * 4 + 3, 2] <- colnames(impute_vars)[i]
  table_birthplace[(i - 1) * 4 + 3, 3] <- "China"
  table_birthplace[(i - 1) * 4 + 3, 4] <- round(coef[4,1], 2)
  table_birthplace[(i - 1) * 4 + 3, 5] <- coef[4,4]
  table_birthplace[(i - 1) * 4 + 3, 6] <- p.adjust(coef[4,4], n = n_compare)
  
  table_birthplace[(i - 1) * 4 + 4, 1] <- "mom.birthplace5"
  table_birthplace[(i - 1) * 4 + 4, 2] <- colnames(impute_vars)[i]
  table_birthplace[(i - 1) * 4 + 4, 3] <- "Other"
  table_birthplace[(i - 1) * 4 + 4, 4] <- round(coef[5,1], 2)
  table_birthplace[(i - 1) * 4 + 4, 5] <- coef[5,4]
  table_birthplace[(i - 1) * 4 + 4, 6] <- p.adjust(coef[5,4], n = n_compare)
  
}

table_birthplace <- table_birthplace %>% 
  mutate(flag = ifelse(p_adj < 0.05, T, 
                     ifelse(abs(Beta) > 2, T, F)))

table_birthplace

filter(table_birthplace, flag == T)$impute_name
```

There is pretty good evidence that maternal birthplace is strongly associated with gestational concentrations of quite a few chemicals (especially mercury, beta-HCH, DDE). 


# Condition ii
No need to assess this, all of the candidate auxiliary variables I came up with met condition i. 


# Conclusions
All of the candidate auxiliary variables I proposed meet at least one of they two conditions for being used to aid in MICE imputation. As such, I will utilize the following auxiliary variables in my analysis:

1) birth weight
2) gestational age
3) alcohol consumption during pregnancy (yes/ no)
4)  Pre-pregnancy BMI
5) *Continuous* third trimester plasma total folate concentrations 
6) *Continuous* FA supplementation
7) Maternal birthplace


```{r}

```







