---
title: "Supplementary tables 2025"
author: "Josh Alampi"
date: "2025-04-25"
output: html_document
---

# load
```{r}
#clear workspace
rm(list=ls(all=TRUE))

# load packages and functions
source(here::here("libraries.R"))
# source("functions/ggplot functions.R")
source("functions/analysis functions.R")

chemical_info <- readxl::read_xlsx(here::here("data", "chemical info.xlsx"))
```

# functions

## Prep for flextable
Converts long results into a wide table (one column for each set of weights)
```{r}
make_wide <- function(weights, clean_results, k, col_names_a, col_names_b, 
                      cell_1_1_text = "Ψ (95% CI)ᵃ", name_1stcol = "   ",
                      cell_2_2_text = "Weights",
                      chemical_info) {
  
  if (k > 1){
    combinations <- expand.grid(col_names_a, col_names_b)
    combinations <- combinations[order(combinations$Var1, combinations$Var2), ]
    names_vector <- paste0(combinations$Var1, "_", combinations$Var2)
  } else {
    names_vector <- col_names_a
  }
  
  num_cols <- 1 + 5 * k
  
  table <- setNames(data.frame(matrix(data = "", nrow = 18, ncol = num_cols)), 
                    c(name_1stcol, names_vector)) #set column names
  
  # Store results
  table[1, 1]   <- cell_1_1_text
  table[1, 2:num_cols] <-  clean_results 
  
  # Store weights
  table[2, 1] <- "Biomarker names"
  table[2, 2] <- cell_2_2_text
  table[3:18, 1]  <- chemical_info[, 1] # Name
  
  for (i in 1:k){
    these_weights <- weights[,i + 1] # extract column
    
    table[3:6, 1 + i]         <- these_weights[1:4]   # Metals 
    table[7:10, 1 + i + k]    <- these_weights[5:8]   # OCPs
    table[11:13, 1 + i + 2*k] <- these_weights[9:11]  # PFAS
    table[14:17, 1 + i + 3*k] <- these_weights[12:15] # PCBs
    table[7:18, 1 + i + 4*k]  <- these_weights[16:27] # POPs
  }
  
  return(table)
}
```

## Make flextable for weights
```{r}
make_weights_flextable <- function(.data, k = 1, 
                             title, footer) {
  table <- .data
  length <- dim(table)[1]
  width  <- dim(table)[2]
  # width  <- 1 + 5 * k
  vert_lines <- seq(from = 1, by = k, length.out = 5)
  
  vert_lines_i <- ifelse(k > 1, c(2:4), c(2))
  
  flex <- flextable(table)

  if(k != 1){
    flex <- flex %>%
      separate_header()
  }
  
  flex <- flex %>%

    # align header
    align(align = "center", part = "header") %>% # to the center
    align(align = "left", part = "header", j = 1) %>% # except the first column

    # align body
    align(align = "center", part = "body") %>% # to the center
    align(align = "left", part = "body", j = 1) %>% # except the first column

    # # Fix the "weights" sub-heading
    merge_at(i = 2, j = 2:width) %>%
    hline(i = c(1, 2)) %>% # add horizontal lines
    
    # Title and bottom caption
    add_header_lines(title, top = T) %>%
    align(align = "left", i = 1, part = "header") %>% # Align title to the left
    add_footer_lines(value = footer) %>% 

    # Add vertical lines to separate mixtures
    vline(j = vert_lines, i = c(1, 3:length), part = "body") %>% 
    vline(j = 1, i = 2, part = "body") %>% # Next to biomarker names
    
    vline(j = vert_lines, i = vert_lines_i, part = "header") # 2nd rows if k = 1, 2nd + 3rd rows otherwise
  
  if(k != 1){
    flex <- flex %>%
      hline(i = 2, j = 1:width, part = "header", border = fp_border_default()) %>% 
      vline(j = vert_lines, i = 3, part = "header")
  }
  
  return(flex)
}
```


## Make final flextables
Uses the previous 2 functions. Using this function saves a lot of code. 
```{r}
make_mix_flextable <- function(clean_res, weights,
                               mod_var_name, k, filter = T,
                               chemical_info, title, footer, 
                               
                               col_names_a = NULL, col_names_b = "MISSING",
                               cell_1_1_text = "Ψ (95% CI)ᵃ", name_1stcol = "   ",
                               cell_2_2_text = "Weights",
                               manual_width = F) {
  # Prep
  if(is.null(col_names_a) == T){
    col_names_a <- c("Metals", "OC Pesticides", "PFAS", "PCBs", "All POPs")
  }
  
  # If I need to filter so only the mod variable is 
  if(filter == T){
    weights <- weights %>% 
      filter(mod_var == mod_var_name) %>% 
      pivot_wider(names_from = mod_level, values_from = weight) %>% 
      select(-c(mod_var, mixture_name)) %>% 
      as.data.frame()
  
    clean_res <- clean_res %>% 
      filter(mod_var == mod_var_name) %>% 
      ungroup() %>% 
      dplyr::select(-c(mod_var)) %>% 
      t()
  }
  
  flex <- make_wide(weights = weights, clean_results = clean_res, 
                    k = k, 
                    col_names_a = col_names_a, col_names_b = col_names_b,
                    cell_1_1_text = cell_1_1_text,
                    name_1stcol = name_1stcol,
                    cell_2_2_text = cell_2_2_text,
                    chemical_info) %>% 
    make_weights_flextable(k = k, 
                           title = title, footer = footer)
  
  if(manual_width == F){
    flex <- flex %>% 
      width(j = c(1:(k*5 +1)), 
          width = c(1, rep(0.6, (k*5))), 
          unit = "in")
  }
    
  
  return(flex)
  
}
```

# Prep
```{r}
results_round <- 1 # The number of decimal places to round results to
```

## Category names
```{r}
# mixture_names <- c("Metals", "OC Pesticides", "PFAS", "PCBs", "All POPs")
fa_names <- c("<400", "400-1000", ">1000")
pl_fol_names <- c("<10ᵗʰ %ile", "10ᵗʰ-80ᵗʰ %ile", ">80ᵗʰ %ile")
sex2_names <- c("Male", "Female")
umfa_names <- c("≤80ᵗʰ %ile", ">80ᵗʰ %ile")
wqs_names <- c("(+)", "(-)")
```

## Titles
```{r}
title_qgcomp <- "Table S2. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation, including weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_sex2 <- "Table S3. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation and assessing modification by child sex, including quantile g-computation weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_fa <- "Table S4. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation and assessing modification by gestational folic acid supplementation, including quantile g-computation weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_pl_fol <- "Table S5. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation and assessing modification by plasma total folate concentrations, including quantile g-computation weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_wqs <- "Table S6. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using weighted quantile sum regression, including weighted quantile sum weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_umfa <- "Table S7. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation and assessing modification by plasma unmetabolized folic acid concentrations, including quantile g-computation weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_qgcomp_fish <- "Table S8. Adjustedᵃ associations (additionally controlling for gestational fish consumption) between chemical mixtures and SRS-2 T-scores using quantile g-computation, including quantile g-computation weights, the MIREC study, Canada, 2008-2011 (n = 601)."

title_qgcomp_no_ipw <- "Table S9. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation without inverse probability weighting, the MIREC study, Canada, 2008-2011 (n = 601)."

title_fa_no_ipw<- "Table S10. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation and assessing modification by gestational folic acid supplementation without inverse probability weighting, the MIREC study, Canada, 2008-2011 (n = 601)."

title_pl_fol_no_ipw <- "Table S11. Adjustedᵃ associations between chemical mixtures and SRS-2 T-scores using quantile g-computation and assessing modification by plasma total folate concentrations without inverse probability weighting, the MIREC study, Canada, 2008-2011 (n = 601)."

```

## Footers
```{r}
controls_for <- function(vars, IPW = T) {
  output <- paste0("a: Controls for the following variables: ", 
                   vars, 
                   ", child age at SRS-2 assessment, HOME score, household income, relationship status, maternal education, maternal race, maternal age, parity, smoking status, city of residence, and year of enrollment. Effect estimates are pooled across 10 multiply imputed datasets.", 
                   ifelse(IPW == T, 
                          " Stabilized inverse probability weights are applied.", 
                          " Stabilized inverse probability weights are not applied."))
}

fa_footer <- "b: Folic acid supplementation was primarily measured via a survey conducted at 16 weeks gestation, which queried intake in the past 30 days. We also used data from the 24-hour recall version of this survey and a questionnaire completed at study enrollment (6-13 weeks gestation)."
pl_fol_footer <- "b: The sum of 5-formyl-THF, 5-10-methylene-THF, THF, UMFA, and 5-methyl-THF."
weights_footer_b <- "b: Only the weights from the first MICE imputation, not the pooled weights, are displayed."
weights_footer_c <- "c: Only the weights from the first MICE imputation, not the pooled weights, are displayed."
weights_footer_wqs <- "b: Weights are averaged across 10 multiply imputed datasets."


# abbrev_indiv <- "Abbreviations: BDE, brominated diphenyl ether; CI; Confidence interval; DDE, Dichlorodiphenyldichloroethylene; HOME, Home Observation for Measurement of the Environment; MIREC, Maternal-Infant Research on Environmental Chemicals Study; PCB, Polychlorinated biphenyl; PFHxS, Perfluorohexanesulfonic acid; PFOA, Perfluorooctanoic acid; PFOS, Perfluorooctanesulfonic acid; SRS-2, Social Responsiveness Scale-2; β-HCH, β-Hexachlorocyclohexane."

abbrev_qgcomp <- "Abbreviations: BDE, brominated diphenyl ether; CI; Confidence interval; DDE, Dichlorodiphenyldichloroethylene; HOME, Home Observation for Measurement of the Environment; MICE, Multiple imputation by chained equations; MIREC, Maternal-Infant Research on Environmental Chemicals Study; OC, Organochlorine; PCB, Polychlorinated biphenyl; PFAS, Per- and polyfluoroalkyl substances; PFHxS, Perfluorohexanesulfonic acid; PFOA, Perfluorooctanoic acid; PFOS, Perfluorooctanesulfonic acid; POP, Persistent organic pollutant; SRS-2, Social Responsiveness Scale-2; β-HCH, β-Hexachlorocyclohexane."

abbrev_pl_fol <- "Abbreviations: BDE, brominated diphenyl ether; CI; Confidence interval; DDE, Dichlorodiphenyldichloroethylene; HOME, Home Observation for Measurement of the Environment; MICE, Multiple imputation by chained equations; MIREC, Maternal-Infant Research on Environmental Chemicals Study; OC, Organochlorine; PCB, Polychlorinated biphenyl; PFAS, Per- and polyfluoroalkyl substances; PFHxS, Perfluorohexanesulfonic acid; PFOA, Perfluorooctanoic acid; PFOS, Perfluorooctanesulfonic acid; POP, Persistent organic pollutant; THF, Tetrahydrofolate; UMFA, Unmetabolized folic acid; SRS-2, Social Responsiveness Scale-2; β-HCH, β-Hexachlorocyclohexane; %ile, Percentile."

abbrev_umfa <- "Abbreviations: BDE, brominated diphenyl ether; CI; Confidence interval; DDE, Dichlorodiphenyldichloroethylene; HOME, Home Observation for Measurement of the Environment; MICE, Multiple imputation by chained equations; MIREC, Maternal-Infant Research on Environmental Chemicals Study; OC, Organochlorine; PCB, Polychlorinated biphenyl; PFAS, Per- and polyfluoroalkyl substances; PFHxS, Perfluorohexanesulfonic acid; PFOA, Perfluorooctanoic acid; PFOS, Perfluorooctanesulfonic acid; POP, Persistent organic pollutant; SRS-2, Social Responsiveness Scale-2; β-HCH, β-Hexachlorocyclohexane; %ile, Percentile."

abbrev_wqs <- "Abbreviations: BDE, brominated diphenyl ether; CI; Confidence interval; DDE, Dichlorodiphenyldichloroethylene; HOME, Home Observation for Measurement of the Environment; MICE, Multiple imputation by chained equations; MIREC, Maternal-Infant Research on Environmental Chemicals Study; OC, Organochlorine; PCB, Polychlorinated biphenyl; PFAS, Per- and polyfluoroalkyl substances; PFHxS, Perfluorohexanesulfonic acid; PFOA, Perfluorooctanoic acid; PFOS, Perfluorooctanesulfonic acid; POP, Persistent organic pollutant; SRS-2, Social Responsiveness Scale-2; β-HCH, β-Hexachlorocyclohexane."


footer_qgcomp <- paste0(controls_for("child sex, gestational folic acid supplementation"), "\n", 
                    weights_footer_b, "\n", abbrev_qgcomp)
footer_sex2 <- paste0(controls_for("gestational folic acid supplementation"), "\n", 
                    weights_footer_b, "\n", abbrev_qgcomp)
footer_fa <- paste0(controls_for("child sex"), "\n", 
                    fa_footer, "\n", 
                    weights_footer_c, "\n", abbrev_qgcomp)
footer_pl_fol <- paste0(controls_for("child sex"), "\n", 
                    pl_fol_footer, "\n", 
                    weights_footer_c, "\n", abbrev_pl_fol)
footer_wqs <- paste0(controls_for("child sex, gestational folic acid supplementation"), "\n",
                    weights_footer_wqs, "\n", abbrev_wqs)
footer_umfa <- paste0(controls_for("child sex"), "\n", 
                    weights_footer_b, "\n", abbrev_umfa)
footer_qgcomp_fish <- paste0(controls_for("gestational fish consumption, child sex, gestational folic acid supplementation"), "\n", 
                    weights_footer_b, "\n", abbrev_qgcomp)

footer_qgcomp_no_ipw <- paste0(controls_for("child sex, gestational folic acid supplementation", IPW = F), "\n", 
                    weights_footer_b, "\n", abbrev_qgcomp)
footer_fa_no_ipw <- paste0(controls_for("child sex", IPW = F), "\n", 
                    fa_footer, "\n", 
                    weights_footer_c, "\n", abbrev_qgcomp)
footer_pl_fol_no_ipw <- paste0(controls_for("child sex", IPW = F), "\n", 
                    pl_fol_footer, "\n", 
                    weights_footer_c, "\n", abbrev_pl_fol)



```

## set flextable defaults
```{r}
init_flextable_defaults()

set_flextable_defaults(
  font.size = 9.5, font.family = "Calibri",
  font.color = "black",
  table.layout = "fixed",
  border.color = "black",
  line_spacing = 1,
  padding.top = 0, padding.bottom = 0,
  padding.left = 0, padding.right = 0)

```

# load and clean data

## qgcomp
```{r}
qgcomp_res <- read.csv("output/analysis/raw res_qgcomp_ipw.csv") %>% 
  mutate(psi = format(round(psi, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb = format(round(lb, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub = format(round(ub, results_round), nsmall = results_round, trim =T))  
  
qgcomp_weights <- read.csv("output/analysis/raw weights_qgcomp_ipw.csv") %>% 
  mutate(weight = round(weight, 2)) %>% 
  filter(imputation_number == 1) %>% 
  select(-c(imputation_number, mixture_name))

# clean
qgcomp_clean_res <- qgcomp_res %>% # Extract qgcomp results
  transmute(res = paste0(psi, "\n(", lb, ", ", ub, ")")) %>% # Format
  t()
```

## qgcomp fish
```{r}
qgcomp_res_fish <- read.csv("output/analysis/raw res_qgcomp_fish_ipw.csv") %>% 
  mutate(psi = format(round(psi, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb = format(round(lb, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub = format(round(ub, results_round), nsmall = results_round, trim =T))  
  
qgcomp_weights_fish <- read.csv("output/analysis/raw weights_qgcomp_fish_ipw.csv") %>% 
  mutate(weight = round(weight, 2)) %>% 
  filter(imputation_number == 1) %>% 
  select(-c(imputation_number, mixture_name))

# clean
qgcomp_clean_res_fish <- qgcomp_res_fish %>% # Extract qgcomp results
  transmute(res = paste0(psi, "\n(", lb, ", ", ub, ")")) %>% # Format
  t()
```

## qgcomp-int
```{r}
int_res <- read.csv("output/analysis/raw res_qgcomp_int_ipw.csv") %>% 
  mutate(psi = format(round(psi, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb = format(round(lb, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub = format(round(ub, results_round), nsmall = results_round, trim =T)) %>% 
  arrange(factor(mod_var, 
                 c("fol.intake3", "pl_fol3.t1", "sex2")),
          factor(mixture_name, 
                 c("Metals", "OC Pesticides", "PFAS",
                   "PCBs", "All POPs")),
          factor(mod_level, # Set the order with which results are listed (from left to right)
                 c("≤80th %ile", # low UMFA listed first
                   "<400", "400-1000",">1000",
                   "<10th %ile", "10th-80th %ile", ">80th %ile", 
                   # low, medium, high plasma folate; high UMFA listed last
                   "Male", "Female")) )

int_weights <- read.csv("output/analysis/raw weights_qgcomp_int_ipw.csv") %>% 
  mutate(weight = round(weight, 2)) %>% 
  filter(imputation_number == 1) %>% 
  rename(mod_var = mod_var_name) %>% # rename the "mod_var_name" column to "mod_var"
  select(-c(imputation_number))

# Clean
int_clean_res <- int_res %>% 
  group_by(mod_var) %>% 
  transmute(res = paste0(psi, "\n(", lb, ",\n", ub, ")")) # Format

```

## WQS 
```{r}
# load results
wqs_res <- read.csv("output/analysis/raw res_wqs_IPW.csv") %>% 
  mutate(beta_pos = format(round(beta_pos, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb_pos = format(round(lb_pos, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub_pos = format(round(ub_pos, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(beta_neg = format(round(beta_neg, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb_neg = format(round(lb_neg, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub_neg = format(round(ub_neg, results_round), nsmall = results_round, trim =T)) 

wqs_weights <- read.csv("output/analysis/raw pooled weights_wqs_IPW.csv") %>% 
  select(-c(mixture_name)) %>% 
  mutate(mean_weight_pos = round(mean_weight_pos, 2)) %>% 
  mutate(mean_weight_neg = round(mean_weight_neg, 2)) 

# Clean
wqs_clean_res <- wqs_res %>% # Extract qgcomp results
  mutate(res_pos = paste0(beta_pos, "\n(", lb_pos, ",\n", ub_pos, ")")) %>% 
  mutate(res_neg = paste0(beta_neg, "\n(", lb_neg, ",\n", ub_neg, ")")) %>% 
  select(c(res_pos, res_neg)) %>% 
  t() %>% 
  as.vector()
```

## qgcomp WITHOUT IPW
```{r}
# Full sample
qgcomp_res_no_ipw <- read.csv("output/analysis/raw res_qgcomp.csv") %>% 
  mutate(psi = format(round(psi, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb = format(round(lb, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub = format(round(ub, results_round), nsmall = results_round, trim =T))  
  
qgcomp_weights_no_ipw <- read.csv("output/analysis/raw weights_qgcomp.csv") %>% 
  mutate(weight = round(weight, 2)) %>% 
  filter(imputation_number == 1) %>% 
  select(-c(imputation_number, mixture_name))

# clean
qgcomp_clean_res_no_ipw <- qgcomp_res_no_ipw %>% # Extract qgcomp results
  transmute(res = paste0(psi, "\n(", lb, ", ", ub, ")")) %>% # Format
  t()

# Interaction
int_res_no_ipw <- read.csv("output/analysis/raw res_qgcomp_int.csv") %>% 
  mutate(psi = format(round(psi, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(lb = format(round(lb, results_round), nsmall = results_round, trim =T)) %>% 
  mutate(ub = format(round(ub, results_round), nsmall = results_round, trim =T)) %>% 
  arrange(factor(mod_var, 
                 c("fol.intake3", "pl_fol3.t1")),
          factor(mixture_name, 
                 c("Metals", "OC Pesticides", "PFAS",
                   "PCBs", "All POPs")),
          factor(mod_level, # Set the order with which results are listed (from left to right)
                 c("<400", "400-1000",">1000",
                   "<10th %ile", "10th-80th %ile", ">80th %ile")) 
          )

int_weights_no_ipw <- read.csv("output/analysis/raw weights_qgcomp_int.csv") %>% 
  mutate(weight = round(weight, 2)) %>% 
  filter(imputation_number == 1) %>% 
  rename(mod_var = mod_var_name) %>% # rename the "mod_var_name" column to "mod_var"
  select(-c(imputation_number))

# Clean
int_clean_res_no_ipw <- int_res_no_ipw %>% 
  group_by(mod_var) %>% 
  transmute(res = paste0(psi, "\n(", lb, ",\n", ub, ")")) # Format
```

# Make flextables

## qgcomp 
```{r}
flex_qgcomp <- make_mix_flextable(clean_res = qgcomp_clean_res, weights = qgcomp_weights, 
                   k = 1, chemical_info = chemical_info, filter = F, manual_width = T,
                   col_names_b = wqs_names, title = title_qgcomp, footer = footer_qgcomp,
                   name_1stcol = "Mixture name",
                   cell_2_2_text = "Weightsᵇ") %>% 
  set_table_properties(layout = "autofit", width = 1) 

flex_qgcomp_fish <- make_mix_flextable(clean_res = qgcomp_clean_res_fish, weights = qgcomp_weights_fish, 
                   k = 1, chemical_info = chemical_info, filter = F, manual_width = T,
                   col_names_b = wqs_names, title = title_qgcomp_fish, footer = footer_qgcomp_fish,
                   name_1stcol = "Mixture name",
                   cell_2_2_text = "Weightsᵇ") %>% 
  set_table_properties(layout = "autofit", width = 1) 

flex_qgcomp
flex_qgcomp_fish
```

## qgcomp-interaction 
```{r}
flex_sex2 <- make_mix_flextable(clean_res = int_clean_res, weights = int_weights, 
                   mod_var_name = "sex2", k = 2, chemical_info = chemical_info, 
                   col_names_b = sex2_names, title = title_sex2, footer = footer_sex2,
                   name_1stcol = "Mixture name_Child sex",
                   cell_2_2_text = "Weightsᵇ")

flex_fa <- make_mix_flextable(clean_res = int_clean_res, weights = int_weights, 
                   mod_var_name = "fol.intake3", k = 3, chemical_info = chemical_info, 
                   col_names_b = fa_names, title = title_fa, footer = footer_fa,
                   name_1stcol = "Mixture name_FA supplementationᵇ (µg/day)",
                   cell_2_2_text = "Weightsᶜ")

flex_pl_fol <- make_mix_flextable(clean_res = int_clean_res, weights = int_weights, 
                   mod_var_name = "pl_fol3.t1", k = 3, chemical_info = chemical_info, 
                   col_names_b = pl_fol_names, title = title_pl_fol, footer = footer_pl_fol,
                   name_1stcol = "Mixture name_Plasma total folate concentrationᵇ",
                   cell_2_2_text = "Weightsᶜ")

flex_umfa <- make_mix_flextable(clean_res = int_clean_res, weights = int_weights, 
                   mod_var_name = "umfa2.t1", k = 2, chemical_info = chemical_info, 
                   col_names_b = umfa_names, title = title_umfa, footer = footer_umfa,
                   name_1stcol = "Mixture name_Plasma unmetabolized folic acid concentrations",
                   cell_2_2_text = "Weightsᵇ")

flex_sex2
flex_fa
flex_pl_fol
flex_umfa
```

## WQS
```{r}
flex_wqs <- make_mix_flextable(clean_res = wqs_clean_res, weights = wqs_weights, 
                               k = 2, chemical_info = chemical_info, filter = F,
                               col_names_b = wqs_names, title = title_wqs, footer = footer_wqs,
                               name_1stcol = "Mixture name_Partial effect",
                               cell_1_1_text = "β (95% CI)ᵃ",
                               cell_2_2_text = "Weightsᵇ")

flex_wqs
```

##qgcomp WITHOUT IPW
```{r}
flex_qgcomp_no_ipw <- make_mix_flextable(clean_res = qgcomp_clean_res_no_ipw, weights = qgcomp_weights_no_ipw, 
                   k = 1, chemical_info = chemical_info, filter = F, manual_width = T,
                   col_names_b = wqs_names, title = title_qgcomp_no_ipw, footer = footer_qgcomp_no_ipw,
                   name_1stcol = "Mixture name",
                   cell_2_2_text = "Weightsᵇ") %>% 
  set_table_properties(layout = "autofit", width = 1) 

flex_fa_no_ipw <- make_mix_flextable(clean_res = int_clean_res_no_ipw, weights = int_weights_no_ipw, 
                   mod_var_name = "fol.intake3", k = 3, chemical_info = chemical_info, 
                   col_names_b = fa_names, title = title_fa_no_ipw, footer = footer_fa_no_ipw,
                   name_1stcol = "Mixture name_FA supplementationᵇ (µg/day)",
                   cell_2_2_text = "Weightsᶜ")

flex_pl_fol_no_ipw <- make_mix_flextable(clean_res = int_clean_res_no_ipw, weights = int_weights_no_ipw, 
                   mod_var_name = "pl_fol3.t1", k = 3, chemical_info = chemical_info, 
                   col_names_b = pl_fol_names, title = title_pl_fol_no_ipw, footer = footer_pl_fol_no_ipw,
                   name_1stcol = "Mixture name_Plasma total folate concentrationᵇ",
                   cell_2_2_text = "Weightsᶜ")


flex_qgcomp_no_ipw
flex_fa_no_ipw
flex_pl_fol_no_ipw
```


# Put together
```{r}
titles <- setNames(data.frame(matrix(data = NA, nrow = 16, ncol = 2)), #make dataframe
                                        c("Item", "Page number")) #set column names
titles[1,1] <- "Table of contents"
titles[2,1] <- "Appendix 1: Further details on our use of multiple imputation by chained equations."
titles[3,1] <- "Table S1. Comparison of study and full sample's sociodemographic characteristics, MIREC study, Canada, 2008-11."
titles[4,1] <- title_qgcomp
titles[5,1] <- title_sex2
titles[6,1] <- title_fa
titles[7,1] <- title_pl_fol
titles[8,1] <- title_wqs
titles[9,1] <- title_umfa
titles[10,1] <- title_qgcomp_fish
titles[11,1] <- title_qgcomp_no_ipw
titles[12,1] <- title_fa_no_ipw
titles[13,1] <- title_pl_fol_no_ipw
titles[14,1] <- "Figure S1. Flow chart of study participants in sample, the MIREC Study, Canada, 2008-11."
titles[15,1] <- "Figure S2. Directed acyclic graph depicting our assumptions about the relationship between gestational environmental chemical mixtures and autistic behaviors."
titles[16,1] <- "References"

titles <- titles %>% 
  flextable() %>% 
  set_table_properties(layout = "autofit", width = 1) 
titles
```


```{r}
# Create a Word document
doc <- read_docx() %>%
  body_add_flextable(value = titles) %>% 
  body_add_break() %>% 
  body_add_flextable(value = flex_qgcomp) %>% 
  body_add_break() %>% 
  body_add_flextable(value = flex_sex2) %>%
  body_add_break() %>% 
  
  body_end_section_portrait() %>% 
  body_add_flextable(value = flex_fa) %>% 
  body_add_break() %>% 
  body_add_flextable(value = flex_pl_fol) %>%
  body_add_break() %>% 
  body_end_section_landscape() %>% 
  
  body_add_flextable(value = flex_wqs) %>% 
  body_add_break() %>% 
  body_add_flextable(value = flex_umfa) %>%
  body_add_break() %>% 
  body_add_flextable(value = flex_qgcomp_fish) %>% 
  body_add_break() %>% 
  
  body_add_flextable(value = flex_qgcomp_no_ipw) %>% 
  body_add_break() %>% 
  body_end_section_portrait() %>% 
  body_add_flextable(value = flex_fa_no_ipw) %>% 
  body_add_break() %>% 
  body_add_flextable(value = flex_pl_fol_no_ipw) %>%
  body_end_section_landscape() 

```

# Save
```{r}
# save
base::print(doc, target = "output/supp tables.docx")
base::print(doc, target = paste0("output/analysis/archive/supp tables_", Sys.Date(), ".docx"))
```


```{r}

```

